Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 Moltres.tex
Address fuel utilization question (Closes #64

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained renewed research
interest in the past decade, with many new nuclear companies proposing both
fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_power_corporation_neutronics_2016}. 
Two key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
utilization and no radiation damage constraint on attainable fuel
burn-up. Together, these attributes result in significantly reduced core fissile
inventories and spent nuclear fuel mass 
\cite{gif_generation_2008,gif_generation_2015}.  
Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
burning actinides and extending fuel resources.

@@

Parallelization in Moltres is implemented via LibMesh, which includes a set of
utilities for massively parallel finite element based computations, including
mesh input/output, a finite element library, and an interface for connections with
solver packages. Employing LibMesh provides Moltres
significant flexibility including the ability to swap out solver libraries
such as PetSc, which includes an expanding suite of parallel linear and
nonlinear solvers. Problem domain decomposition relies on LibMesh mesh
adaptation capabilities for running on a specific number of processors and
can either be performed manually before the start of the simulation or
automatically at the parameters of computation.

>>>>

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained
renewed research interest in the past decade, with many new nuclear companies
proposing both fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_power_corporation_neutronics_2016}.
Two key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
utilization and no radiation damage constraint on attainable fuel
burn-up. Together these attributes can result in significantly reduced spent
fuel mass and, in the case of fluoride salt reactors in particular, reduced core
fissile inventories \cite{gif_generation_2008,gif_generation_2015}.  Due to
these characteristics, the \gls{MSR} is potentially uniquely capable of burning
actinides and extending fuel resources.

@@

Parallelization in Moltres is implemented via LibMesh, which includes a set of
utilities for massively parallel finite element based computations, including
mesh input/output, a finite element library, and an interface for connections with
solver packages. Employing LibMesh provides Moltres with
significant flexibility including the ability to swap out solver libraries
such as PetSc, which includes an expanding suite of parallel linear and
nonlinear solvers. Problem domain decomposition relies on LibMesh mesh
adaptation capabilities for running on a specific number of processors and
can either be performed manually before the start of the simulation or
automatically at the parameters of computation.

### 2017-11-27 revise/revise.tex
Just reformat revise.tex to use shorter lines
Address fuel utilization question (Closes #64

\question In the introduction, the authors mention that:
``Two key advantages offered by the fluid-fuelled MSR are improved fuel 
        utilization and no radiation damage constraint on attainable fuel 
        burn-up. Together, these attributes result in significantly reduced 
        core fissile inventories and spent nuclear fuel mass''
However, the fissile inventory is not necessarily related to fuel burnup and fuel utilization. It can actually be  very high in chloride-based fast-spectrum MSRs.
\begin{solution}
        <++>
\end{solution}

@@

\question The proposed scaling test is very limited. Proper scaling tests would require weak and strong scaling tests, an assessment on the impact of the size of problem per core, a separate assessment of intra-node and extra-node scaling, etc. In addition, information should be provided on the employed numerical algorithms and on the parallelization strategy. The authors should either extend significantly the section, or remove it completely.
\begin{solution}
        We performed strong and weak scaling up to 768 cores separately for 
        intra-node and extra-node cases. Parallelization was implemented using 
        LibMesh library for automatic domain decomposition and PetSc 
        library for parallel solution of systems of non-linear equations. 
        Detailed information, including results of the scalind studies, has now 
        been added in the Section 4.3 introduction.
\end{solution}

>>>>

\question In the introduction, the authors mention that: ``Two key advantages
offered by the fluid-fuelled MSR are improved fuel utilization and no radiation
damage constraint on attainable fuel burn-up. Together, these attributes result
in significantly reduced core fissile inventories and spent nuclear fuel mass''
However, the fissile inventory is not necessarily related to fuel burnup and
fuel utilization. It can actually be very high in chloride-based fast-spectrum
MSRs.
\begin{solution}
        We have edited this sentence to read ``Together these attributes can
        result in significantly reduced spent fuel mass and, in the case of
        fluoride salt reactors in particular, reduced core fissile
        inventories'', recognizing that you're quite correct for the chloride salts.
\end{solution}

@@

\question The proposed scaling test is very limited. Proper scaling tests would
require weak and strong scaling tests, an assessment on the impact of the size
of problem per core, a separate assessment of intra-node and extra-node scaling,
etc. In addition, information should be provided on the employed numerical
algorithms and on the parallelization strategy. The authors should either extend
significantly the section, or remove it completely.
\begin{solution}
        We performed strong and weak scaling up to 768 cores separately for
        intra-node and extra-node cases. Parallelization was implemented using
        LibMesh library for automatic domain decomposition and PetSc
        library for parallel solution of systems of non-linear equations.
        Detailed information, including results of the scaling studies, has now
        been added in the Section 4.3 introduction.
\end{solution}
